Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1)

### 2014-03-29 WSSSPE1_report/WSSSPE1_summary_report.tex

% note that paper summaries are available in an earlier commit 
% in James Howison's fork:
% https://github.com/jameshowison/WSSSPE/blob/587705cb6f12f46951e822fdbf5eb72b104fa397/WSSSPE1_report/WSSSPE1_summary_report.tex

@@

@@

\todo{convert this sketch to discussion of policy options}
        Opportunities for Policy interventions:
                Funding agencies
                Journals.  Success of data policies, growth of software policies.
                Promotion and Tenure. Follow lead of Science of Team Science in surveying policies at universities and other institutes.

\todo{review PiratePad notes for other aspects of credit-giving discussed.}
\begin{itemize}

>>>>

\subsection*{Modeling Sustainability}

@@

\subsection*{Credit, Citation, Impact}

@@

\todo{convert this sketch to discussion of policy options}
\begin{verbatim}
        Opportunities for Policy interventions:
                Funding agencies
                Journals.  Success of data policies, growth of software policies.
                Promotion and Tenure. Follow lead of Science of Team Science in surveying policies at universities and other institutes.
\end{verbatim}
\todo{review PiratePad notes for other aspects of credit-giving discussed.}

\subsection*{Implementing Policy}

% note that paper summaries are available in tag jameshowison-paper-summaries: 
% https://github.com/danielskatz/WSSSPE/blob/jameshowison-paper-summaries/WSSSPE1_report/WSSSPE1_summary_report.tex

\item Coral Calero, M. Angeles Moraga, Manuel F. Bertoa. Towards a
  Software Product Sustainability Model~\cite{Calero_WSSSPE}

\item Colin C. Venters, Lydia Lau, Michael K. Griffiths, Violeta
  Holmes, Rupert R. Ward, Jie Xu. The Blind Men and the Elephant:
  Towards a Software Sustainability Architectural Evaluation Framework~\cite{Venters_WSSSPE}

\item Marlon Pierce, Suresh Marru, Chris Mattmann. Sustainable
  Cyberinfrastructure Software Through Open Governance~\cite{Pierce_WSSSPE}

\item Daniel S. Katz, David Proctor. A Framework for Discussing
  e-Research Infrastructure Sustainability~\cite{Katz_WSSSPE}

\item Christopher Lenhardt, Stanley Ahalt, Brian Blanton, Laura
  Christopherson, Ray Idaszak. Data Management Lifecycle and Software
  Lifecycle Management in the Context of Conducting Science~\cite{Lenhardt_WSSSPE}

\item Nicholas Weber, Andrea Thomer, Michael Twidale. Niche Modeling:
  Ecological Metaphors for Sustainable Software in Science~\cite{Weber_WSSSPE}
